Parsing Tweets into Universal Dependencies

### 2017-10-26 paper.tex
Noah
fix some errors

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweets treebank ({\sc Tweebank})
which has 12,149 tokens and was created using the 
\citet{Yamada03statisticaldependency} dependencies. Both these
annotation efforts were highly influenced by the PTB whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2017 to July 2017.
The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{graphics/alpha}
	\caption{The effect of $\alpha$ on distillation.}\label{fig:effect-alpha}
\end{figure}

>>>>

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweets treebank ({\sc Tweebank})
which has 12,149 tokens and largely followed the conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
\citet{Yamada03statisticaldependency} dependencies. Both these
annotation efforts were highly influenced by the PTB whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{green}{user at-mention}
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
\end{figure*}

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2016 to July 2016.
The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{graphics/alpha}
	\caption{The effect of $\alpha$ on
          distillation. \nascomment{to do:  please make the font in
            the graphic readable}}\label{fig:effect-alpha}
\end{figure}
